---
title: "Lao Map Boundary for Website"
format: html
execute: 
  echo: false
  warning: false
---

This repository provides administrative boundary maps at the province, district, and village levels based on 2015 data.

Disclaimer: The CRS of these maps was modified from EPSG:32648 to EPSG:4326 for better compatibility with web mapping. Additionally, some village names have been corrected for typos, and incorrect dcodes allocated to villages have been fixed. 


```{r}
# Import library
library(tidyverse)
library(gt)
library(leaflet)
library(sf)
library(paletteer)
library(htmltools)
library(glue)
```

```{r}
# Read map
map_adm1 <- st_read('map/lao_adm1_province_level.geojson', quiet = TRUE)
map_adm2 <- st_read('map/lao_adm2_district_level.geojson', quiet = TRUE)
map_adm3 <- st_read('map/lao_adm3_village_level.geojson', quiet = TRUE)
```

```{r}
# Set map colour
colour <- paletteer_d("nationalparkcolors::Acadia")
```

```{r}
labels_adm1 <- glue(
  "<strong>Province/ແຂວງ:</strong> {map_adm1$pname} | {map_adm1$l_pname}<br/>
    <strong>Pcode:</strong> {map_adm1$pcode}"
) |>
  lapply(HTML)

labels_adm2 <- glue(
  "<strong>Province/ແຂວງ:</strong> {map_adm2$pname} | {map_adm2$l_pname} <br>
    <strong>Pcode:</strong> {map_adm2$pcode} <br>
    <hr>
    <strong>District/ເມືອງ:</strong> {map_adm2$dname} | {map_adm2$l_dname} <br>
    <strong>Dcode:</strong> {map_adm2$dcode}"
) |>
  lapply(HTML)

labels_adm3 <- glue(
  "<strong>Province/ແຂວງ:</strong> {map_adm3$pname} | {map_adm3$l_pname} <br>
    <strong>Pcode:</strong> {map_adm3$pcode} <br>
    <hr>
    <strong>District/ເມືອງ:</strong> {map_adm3$dname} | {map_adm3$l_dname} <br>
    <strong>Dcode:</strong> {map_adm3$dcode} <br>
    <hr>
    <strong>Village/ບ້ານ:</strong> {map_adm3$vname} | {map_adm3$l_vname} <br>
    <strong>Vcode:</strong> {map_adm3$vcode}"
) |>
  lapply(HTML)
```

## Map Preview


### Province
```{r}
leaflet(map_adm1) |>
  addTiles(group = "OpenStreetMap") |>
  addProviderTiles(providers$CartoDB.Positron, group = "Positron (minimal)") |>
  addPolygons(
    fillColor = colour,
    stroke = TRUE,
    weight = 2,
    color = "white",
    opacity = 1,
    dashArray = "3",
    fillOpacity = .7,
    highlightOptions = highlightOptions(
      weight = 3,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = labels_adm1,
    labelOptions = labelOptions(
      style = list(
        "font-weight" = "normal",
        padding = "3px 8px",
        textsize = "1rem",
        direction = "auto"
      )
    ),
  ) |>
  addLayersControl(
    baseGroups = c(
      "OpenStreetMap",
      "Positron (minimal)"
    ),
    options = layersControlOptions(collapsed = FALSE)
  )
```

### District
```{r}
leaflet(map_adm2) |>
  addTiles(group = "OpenStreetMap") |>
  addProviderTiles(providers$CartoDB.Positron, group = "Positron (minimal)") |>
  addPolygons(
    fillColor = colour,
    stroke = TRUE,
    weight = 2,
    color = "white",
    opacity = 1,
    dashArray = "3",
    fillOpacity = .7,
    highlightOptions = highlightOptions(
      weight = 3,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = labels_adm2,
    labelOptions = labelOptions(
      style = list(
        "font-weight" = "normal",
        padding = "3px 8px",
        textsize = "1rem",
        direction = "auto"
      )
    ),
  ) |>
  addLayersControl(
    baseGroups = c(
      "OpenStreetMap",
      "Positron (minimal)"
    ),
    options = layersControlOptions(collapsed = FALSE)
  )
```

### Village
```{r}
leaflet(map_adm3) |>
  addTiles(group = "OpenStreetMap") |>
  addProviderTiles(providers$CartoDB.Positron, group = "Positron (minimal)") |>
  addPolygons(
    fillColor = colour,
    stroke = TRUE,
    weight = 2,
    color = "white",
    opacity = 1,
    dashArray = "3",
    fillOpacity = .7,
    highlightOptions = highlightOptions(
      weight = 3,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE
    ),
    label = labels_adm3,
    labelOptions = labelOptions(
      style = list(
        "font-weight" = "normal",
        padding = "3px 8px",
        textsize = "1rem",
        direction = "auto"
      )
    ),
  ) |>
  addLayersControl(
    baseGroups = c(
      "OpenStreetMap",
      "Positron (minimal)"
    ),
    options = layersControlOptions(collapsed = FALSE)
  )
```

## Data source

National Geographic Department via [k4d.la](https://k4d.la/)

